Sampling requirements to detect ecosystem change

### 2020-03-16 R/manuscript_draft.Rmd
added a few notes on next steps

- writing intro
- writing methods/results pair of section
- writing discussion
- setting up bibliography system
- Possible journals: Methods Ecology and Evolution, Biological Conservation, *Journal of Environmental Management*, *Environmental Monitoring and Assessment*, BioScience

# Main messages of manuscript

- We can choose the number of samples and effort we use...
- Number of samples required depends on question asked and the time series parameters
- Case study of paleo data shows the utility of iterative sampling in detecting change points
-->

@@

- It is not limited to paleo data
- Depends on the question being asked
- Specific number of samples depends on the system dynamics

>>>>

- clean up introduction
- writing methods/results pair of section
- build out the supplementary material
- run theoretical results for more simulations
- concluding paragraph
- add citations
- Possible journals: Journal of Environmental Management, Environmental Monitoring and Assessment, Ecological Applications

@@
